\section{Overall Description}
\subsection{Product Perspective}
\subsubsection{Scenarios}
\begin{enumerate}
    \item \textbf{User wants to start using the eMall service}\\
    The user Matteo decides that he wants to use the eMall service to 
    take advantage of the efficiency it offers. 
    He launches the service and selects the option to sign up. 
    Matteo then inputs all the relevant information and he is granted access to the service.
    \item \textbf{User books the recharge for his car}\\
    After a long drive, the user Matteo noticies that the level of his battery is low. 
    He stops, takes his phone and launches the eMall service, logs in, and then he is presented with all the nearby stations.
    He then selects a specific timeslot for charging and he is presented with all the available nearby stations.
    He select a station, views all the available eMSPs offers and then picks his preferred one.  
    \item \textbf{User starts the charge}\\
    The user Matteo drives to a station that he has a charge booked with, he then connects his electric 
    vehicle to the booked socket and, after he has left the vehicle, he launches the eMall service and 
    he is presented with the option to start the vehicle's charge. He selects this option and the station initiates charging on the booked socket. eMall than shows the user the time for the full charge of the vehicle. 
    \item \textbf{User is notifies of a finished charge}\\
    After the user Matteo has started to charging process at the station,
     he goes to a nearby cafeteria to have a cup of coffee. When the car has fully charge, the eMall service notifies him on his phone with a push notification.
    \item \textbf{User pays for the service}\\
    The user Matteo, after he has used the eMall service for a successful charge, provided that he has not paid for the service yet,
    launches the app and he is presented with the option to pay for the service, 
    he selects this option and then enters his credit card information.
    The service that processes his payment, and if it is successful he is presented with a success message.
    \item \textbf{User is reminded to charge his electric vehicle}\\
    While the user Matteo is driving, the eMall service monitors the car's battery level, the user's location and his schedule. 
    When the service finds an optimal place to charge, related to schedule, location and state of charge it notifies the user with a push notification.
    Matteo then stops, launches the eMall service and then he is presented with the optimal station to charge with the most convenient eMSP and the best timeslot with respect to his schedule. He then books the charge.
\end{enumerate}
\subsection{Product Functions}
\subsection{User Characteristics}
\subsection{Assumptions, Dependencies and Constraints}